\documentclass{coverletter}

\begin{document}
\textbf{\fontsize{24 pt}{24 pt}\selectfont Alireza Arzehgar}

\textit{Cloud Engineer}

\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.1pt}}
\begin{center}
  \normalsize
  \mbox{\hrefWithoutArrow{mailto:alirezaarzehgar82@gmail.com}{\color{black}{\footnotesize\faEnvelope[regular]}\hspace*{0.13cm}alirezaarzehgar82@gmail.com}}
  \kern 0.25 cm
  \mbox{\hrefWithoutArrow{live:.cid.78363b7f9529229a}{\color{black}{\footnotesize\faSkype}\hspace*{0.13cm}live:.cid.78363b7f9529229a}}
  \\
  \kern 0.25 cm
  \mbox{\hrefWithoutArrow{https://www.linkedin.com/in/alirezaarzehgar/}{\color{black}{\footnotesize\faLinkedinIn}\hspace*{0.13cm}alirezaarzehgar}}
  \kern 0.25 cm
  \mbox{\hrefWithoutArrow{tel:+98-915-509-31-14}{\color{black}{\footnotesize\faPhone*}\hspace*{0.13cm}+989155093114}}
  \kern 0.25 cm
  \mbox{{\color{black}\footnotesize\faMapMarker*}\hspace*{0.13cm}Mashhad}

  \noindent\makebox[\linewidth]{\rule{\paperwidth}{0.1pt}}
\end{center}

\textbf{To}

Snapp

\textit{\today}

\vspace{1cm}
Respected Madam Parisa Naeemi,
\vspace{0.6 cm}
\setlength{\parindent}{20pt}

As a passionate Cloud Engineer with over 4 years of experience, I have been a long-time fan of the Snapp development team.
Working at Snapp feels like a dream, and if given the opportunity,
I would be just as proud to be part of it as I am of my open-source contributions to the Go programming language
and the valuable feedback I've received from senior developers at Google.
I believe this position will make me even happier than I already am, as I am naturally a happy person.
I am a quick learner, and reading technical books is a dopamine source for me.
\\

My journey began at the age of 15 when I wrote my first C code and spent my youth exploring Linux.
4 years ago I got my first job as an Embedded Network Engineer at ZharfPooyan Toos when I was 17.
In ZharfPooyan I worked on routers and switches using C and Unix-related technologies.
I automated performance testing of network appliances and designed a robust network lab here.
\\

After my experience at ZharfPooyan, I became passionate about Cloud Computing and started my new journey
with Golang, Docker and the backend field. But every time I designed a backend solution
I kept in mind simplicity, correctness, being cloud-friendly and scalability.
I start work at Asrez Co companies as a Golang Developer. I learned some cloud-related
concepts and experience developing backend solutions. I developed a monitoring system with
Prometheus \& Grafana to visualize over 10K loads per minute.
Like Asrez I was a Golang developer in Arttizens but I can mention that CI/CD and automated processes are one of my
important roles here.
\\

\setlength{\parindent}{0pt}

Thank you for your time and attention.
\\

Sincerely,

Alireza Arzehgar

\end{document}
