\documentclass{engineercv}

\begin{document}
\begin{center}
  \textbf{\fontsize{24 pt}{24 pt}\selectfont Alireza Arzehgar}

  \vspace{0.3 cm}

  \normalsize
  \mbox{{\color{black}\footnotesize\faMapMarker*}\hspace*{0.13cm}Mashhad}
  \kern 0.25 cm
  \mbox{\hrefWithoutArrow{mailto:alirezaarzehgar82@gmail.com}{\color{black}{\footnotesize\faEnvelope[regular]}\hspace*{0.13cm}alirezaarzehgar82@gmail.com}}
  \kern 0.25 cm
  \mbox{\hrefWithoutArrow{tel:+98-915-509-31-14}{\color{black}{\footnotesize\faPhone*}\hspace*{0.13cm}989155093114}}
  \kern 0.25 cm
  \mbox{\hrefWithoutArrow{https://www.linkedin.com/in/alirezaarzehgar/}{\color{black}{\footnotesize\faLinkedinIn}\hspace*{0.13cm}alirezaarzehgar}}
  \kern 0.25 cm
  \mbox{\hrefWithoutArrow{https://github.com/alirezaarzehgar}{\color{black}{\footnotesize\faGithub}\hspace*{0.13cm}alirezaarzehgar}}
\end{center}

\vspace{0.3 cm - 0.3 cm}

\section{SUMMARY}

Software developer with 4+ years of experience, known for loving his job and being interested in learning new things.
Skilled in problem-solving and research. Highly interested in open-source and UNIX systems.
A good student when learning from experts and a good teacher for beginners.
I enjoy reading technical books and talking about what I learned and observed from the binary world.

\section{SKILLS}

\begin{itemize}
  \item \textbf{Go programming:} Experience in developing efficient and high-quality Go software.
  \item \textbf{UNIX Systems:}  Love UNIX systems for 7+ years. Experience in maintaining production-grade Linux/FreeBSD platforms.
  \item \textbf{C programming:} Good understanding of low-level stuff and experience in developing and maintaining C code bases.
    Automate my tasks using Bash.
  \item \textbf{Database:} Experience with SQL and NoSQL databases like MySQL, PostgreSQL, and Redis.
  \item \textbf{Project Management \& CI/CD:} Ability to manage projects using Git and CI/CD.
  \item \textbf{Networking:} Enable networking features for UNIX systems and be familiar with CISCO routers.
  \item \textbf{Documentation:} Strong commitment to creating and following technical documentation and processes.
  \item \textbf{R\&D:} Ability to learn new things and design solutions for problems. Passionate about complex tasks.
  \item \textbf{Software design:} Correctness and good software design are the main goals for all of my projects.
\end{itemize}

\section{EXPERIENCE}

\begin{twocolentry}{\textit{Dec 2023 - July 2024}}
  \textbf{Golang Developer}
  \textit{Arttizens}

  \begin{itemize}
    \item Extend exchange infrastructure using microservices. Develop \& maintain 10+ microservices.
      I emphasize a design-first approach and spend time on design correctness. Most of the project times
      spent on designing a correct solution. Create a test infrastructure based on TDD using Postman.
      for integration tests and built-in unit test tools. I'm committed to documenting everything and reporting.
      my activities for the product team.
    \item Make NGINX/NAXI configuration management easier by implementing a WAF system manager.
    \item Develop an exchange match engine.
    \item Design a CRM solution backend for HRM departments compatible with product management needs.
    \item Maintain UNIX servers and virtual machines and keep everyone's connection stable.
    \item Introduce CI/CD to our team and run a GitLab CI instance on our development servers.
      Write pipelines and CI processes for the back-end and front-end teams.
    \item Consultant for project architectures.
  \end{itemize}
  \textbf{Stack:} Go, Python, Bash, Docker, Echo, GORM, Postgres, Redis, NGINX/NAXI, Gitlab CI, Debian, scrum, GNU make.
\end{twocolentry}

\vspace{0.5 cm}

\begin{twocolentry}{\textit{Jul 2023 - dec 2023}}
  \textbf{Golang Developer}
  \textit{Asrez Co}

  \begin{itemize}
    \item Building 10+ high-quality applications and designing solutions based on business needs.
    \item Deploy the developed API in a production environment by configuring servers and running self-deployed
      applications on containers.
    \item Design and implement event-driven solutions for 3 applications.
    \item Add a monitoring feature to capture user activities in a product.
    \item Collaborate in open-source projects of the company.
    \item Add features and refactor existing projects based on new business requirements.
  \end{itemize}
  \textbf{Stack:} Go, Echo, GORM, event-dirven development, NATS, Kafka, RabbitMQ, Docker, Prometheus+Grafana,
  MySQL/Postgres, GNU make.
\end{twocolentry}

\vspace{0.5 cm}

\begin{twocolentry}{\textit{Jul 2021 - jul 2023}}
  \textbf{System Software Developer}
  \textit{ZharfPooyan Toos}

  \begin{itemize}
    \item Maintain physical servers and administrate UNIX systems like FreeBSD and Debian.
      I was responsible for installing, repairing, and configuring some testing environments.
    \item Design a solution for testing the performance of network appliances using TRex and RFC 2544.
    \item Work on the FRR code base to maintain router features.
    \item Port one of the DPDK versions based on infrastructure requirements.
    \item Write technical documentation for other teams to interact with our products.
    \item Work on the AAA feature of the router and L3 layer switch using PAM and FRR.
  \end{itemize}
\end{twocolentry}
\textbf{Stack:} C, Python, Bash, FRR, CISCO TRex, GNU GRUB, Linux, FreeBSD, PAM, DPDK, AAA.

\section{VOLUNTEERING}
\textbf{Open Source:} The most bold volunteering for me is my open-source career. I have 50+ personal open-source projects.
in various topics and with various technologies, from writing C code without glibc to using LLMs.
I have merged commits on 10 open-source projects. My pull requests consist of adding new features.
fixing bugs, fixing linter warnings, or fixing typos.  I'm proud of contributing to the mainstream Golang compiler project.
and other Golang tools that are for the Google team. Collaborating with someone who developed the Go compiler
is so dreamy, and definitely I will continue contributing to the main repository.

\vspace{0.4 cm}

\textbf{Linux Users Group:} I'm an active member of Mashhad LUG. I have 5 lectures on diverse topics.
Also, I translated a guide with the \textit{Linux User Group HOWTO} title to Persian in my repository using LaTeX.
Considering its long paragraphs and complex vocabulary, it was a hard task.

\section{EDUCATION}

\begin{twocolentry}{\textit{Aug, 2022 - Now}}
  \textbf{Bachelor, Computer Engineering}
  \textit{Azad University of Mashhad}

  \vspace{0.2 cm}
  Here are my activities during the 9-month career gap that I spent at university.
  \vspace{0.2 cm}

  \begin{itemize}
    \item \textbf{Contribute to the Go programming language with 3 merged commits.}
    \item Write many LaTeX papers.
    \item Translate the HOW-TO USERS GROUP manual to Persian.
    \item Implement knowledge to graph the system using LLM.
    \item Reading books about software design stuff like DDD, TDD, and design patterns.
  \end{itemize}
\end{twocolentry}

\end{document}
